Final_Project_Work_HW2_JaJuArEm

### 2022-09-29 Final_Project_Work_HW2.Rmd
First push

imdb_clean$Runtime <- runtime_clean

@@

```{r}
full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues, maybe now
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors())

>>>>

imdb_clean$Runtime <- runtime_clean
```

@@

```{r}
full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues, maybe this will work
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors())
